Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-27 TACAS2018/paper.tex
sec 6

  \path[->] (v1) edge (q1.south);
  \path[->] (v2) edge (q2.south);
  \path[->] (vt) edge (lag.south);
  \path[->] (v1p) edge (o2.north);
  \path[->] (v2p) edge (circle.north);
  \path[->] (r) edge (gain.west);
  \path[->] (gain.east) edge (circle.west);
  \path[->] (circle.east) edge (q2.west);
  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (C.west)
   (C.east) edge (lag.west)
   (lag.east) edge (switch1.west)
   (switch2) edge (q1.west);
  \path
   (q1.east) edge (ykeast)
   (ykeast) edge (o2east);
  \path       (uksouth) edge (bdwest);
  \path[->] (bdwest) edge (Bd.west);
  \path
   (Bd.east) edge (o1.west)
   (o1.east) edge (delay.west)
   (xdsouth) edge (adeast)
   (adeast) edge (Ad.east)
   (Ad.west) edge (adwest)
   (adwest) edge (o1.south)
   (o2.west) edge node {$\vec{y}_e$} (Ld.east)
   (Ld.west) edge (ldwest)
   (ldwest) edge (o1.north)
   (delay.east) edge (Cd.west)
   (Cd.north) edge (o2.south)
   (o2east) edge (o2.east)
   (xdsouth) edge (fbsouth)
   (fbsouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path[->] (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain (identified by the subindex $\langle C \rangle$), whereas the plant is continuous \label{fig:observersystem2}}
\end{figure*}

@@

 Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as described below.
We assume that the system has no inputs, and its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.

 \begin{theorem}
 The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$,
 evaluated at time $T$ is
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
 \mat{A}_{T}&= \mat{S}
 \left [ \begin{array}{cccc}
 e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
\vdots & & \ddots & \vdots \\
0 & \cdots & 0  &e^{T\lambda_i} \\
\end{array} \right ]
 \mat{S}^{-1}
 \label{eq:continuous_tube_dyn}\\
 &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
 \end{align}
$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  
%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x} \text{ with } T \in \mathbb{R}^+$ is the state of the system at time $t=T$.
 \end{corollary}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Next, we are interested in studying models with parametric inputs, 
 which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}$. 
 For such models, a the state $\vec{x}_T$ is computed next.  
\begin{theorem}
The state of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$ is 
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
 \end{align}
 where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}
 \footnote{when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
 then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
 \end{corollary}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}

@@

%
\begin{theorem}
The expression
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
 with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn}, 
 and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, 
 and $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics with sample time $T_s$, 
 is the state of the model 
 \begin{align}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s. 
 \end{align}
 \end{theorem}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}

>>>>

  \path[->] (v1) edge (q1.south);
  \path[->] (v2) edge (q2.south);
  \path[->] (vt) edge (lag.south);
  \path[->] (v1p) edge (o2.north);
  \path[->] (v2p) edge (circle.north);
  \path[->] (r) edge (gain.west);
  \path[->] (gain.east) edge (circle.west);
  \path[->] (circle.east) edge (q2.west);
  \path       (q2.east) edge (zoh.west);
  \path[->] (zoh.east) edge (B.west);
  \path
   (B.east) edge (p1.west)
   (p1.east) edge (int.west)
   (xsouth) edge (aeast)
   (aeast) edge (A.east)
   (A.west) edge (awest)
   (awest) edge (p1.south)
   (int.east) edge (C.west)
   (C.east) edge (lag.west)
   (lag.east) edge (switch1.west)
   (switch2) edge (q1.west);
  \path
   (q1.east) edge (ykeast)
   (ykeast) edge (o2east);
  \path       (uksouth) edge (bdwest);
  \path[->] (bdwest) edge (Bd.west);
  \path
   (Bd.east) edge (o1.west)
   (o1.east) edge (delay.west)
   (xdsouth) edge (adeast)
   (adeast) edge (Ad.east)
   (Ad.west) edge (adwest)
   (adwest) edge (o1.south)
   (o2.west) edge node {$\vec{y}_e$} (Ld.east)
   (Ld.west) edge (ldwest)
   (ldwest) edge (o1.north)
   (delay.east) edge (Cd.west)
   (Cd.north) edge (o2.south)
   (o2east) edge (o2.east)
   (xdsouth) edge (fbsouth)
   (fbsouth) edge (kdsouth);
  \path[->]  (kdsouth) edge (Kd.south);
  \path[->] (Kd.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-loop digital control system with an observer, where the controller and the observer (bottom part) are implemented in a discrete domain (quantities within this domain are identified by the index $\langle C \rangle$), whereas the plant is continuous \label{fig:observersystem2}}
\end{figure*}

@@

 Given a specific time $T$, the state $\vec{x}(t=T)$ can be expressed as a linear function of $\vec{x}_0$ as shown below.
We assume that the system has no inputs, so its dynamics are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$.

 \begin{theorem}
 The solution to the differential equation $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$, where $\mat{A}=\mat{S}\mat{J}\mat{S}^{-1}$,
 evaluated at time $T$ is
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_{T}\vec{x} (0)\\
 \mat{A}_{T}&= \mat{S}
 \left [ \begin{array}{cccc}
 e^{T\lambda_1}  & s_1\frac{T^{1}e^{T\lambda_i}}{(2)!} & \hdots  & s_i\frac{T^{p-1}e^{T\lambda_i}}{(p-i)!} \\
0 & e^{T\lambda_i}  & s_i\frac{T^{j-i}e^{T\lambda_i}}{(j-i)!} & \vdots \\
\vdots & & \ddots & \vdots \\
0 & \cdots & 0  &e^{T\lambda_i} \\
\end{array} \right ]
 \mat{S}^{-1}
 \label{eq:continuous_tube_dyn}\\
 &\text{where } s_i=\left\{\begin{array}{cc}1&\quad gm(\lambda_i)>1\\0&\quad gm(\lambda_i)=1\end{array}\right.,\nonumber
 \end{align}
$\lambda_i$ are the eigenvalues of $\mat{A}$, and $gm(\lambda_i)$ is the geometric multiplicity of $\lambda_i$.  
%$\vec{x}_T$ is the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time t=T.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and there exists a discrete dynamics matrix for a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x} \text{ with } T \in \mathbb{R}^+_0$ is the state of the system at time $t=T$.
 \end{corollary}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 \subsection{Accelerated dynamics for models with parametric inputs}\label{sec:real_discrete_param_inputs}
 %+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
 Next, we are interested in studying models with parametric inputs, 
 which are described by $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$, where $\forall t\geq 0, \mat{B}\vec{u}(t)=\vec{u}$. 
 \note{you mean u(t) = u?}
 For such models, a the state $\vec{x}_T$ is computed next.  
\begin{theorem}
The state of the model $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)$ at time $T$ given a parametric input $\vec{u}$ is 
 \begin{align}
 \vec{x}_T&=\vec{x}(t=T)=\mat{A}_T\vec{x}_0 + \mat{B}_T\vec{u} \text{ where } \mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B} 
 \end{align}
 where $\forall t \leq T,\ \vec{u}(t)=\vec{u}$, and $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn} \note{pls no fwd ref to the appendix- can you use (8)?}
 \footnote{when $\mat{A}$ is not invertible, we use $\left[\begin{array}{cc}\mat{A}_T&\mat{B}_T\\ 0&\mat{I}\end{array}\right]=e^{\left[\begin{array}{cc}\mat{A}&\mat{B}\\0&0\end{array}\right]}$}.
 \end{theorem}
 \begin{corollary}
 If $\mat{J}$ is diagonal and given a sampling time $T_d$ such that $A_d=e^{\mat{A} T_d}$, 
 then $\vec{x}_T=A_d^{\frac{T}{T_d}}\vec{x}+(\mat{I}-\mat{A}_d^{\frac{T}{T_d}}\mat{B}_d\vec{u}) \text{ with } T \in \mathbb{R}_0^+$ \note{here there must be an x that is actually a x0?} (where $\mat{A}_d^{\frac{T}{T_d}} = e^{log(\mat{A}_d) \frac{T}{T_d}} = e^{\mat{A} T}$) is the state of the system at time $T$.
 \end{corollary}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}

@@

%
\begin{theorem}
The expression
 \begin{align}
 \vec{x}_{T} &= (\mat{A}_{T-kT_s}-\mat{B}_{T-kT_s}\mat{K}) (\mat{A}_d-\mat{B}_d\mat{K})^k\vec{x}_0, 
 \label{eq:cyber_feedback}
 \end{align}
 with $\mat{A}_T$ as in \eqref{eq:continuous_tube_dyn} \note{no ref to appendix}, 
 and where $\mat{B}_T=\mat{A}^{-1}(\mat{I}-\mat{A}_T)\mat{B}$, 
 and $\mat{A}_d, \mat{B}_d$ describe the discretized plant dynamics with sample time $T_s$, 
 is the state of the model 
 \begin{align}
 \dot{\vec{x}}(t) = \mat{A}\vec{x}(t)+\mat{B}\vec{u}(t), \quad 
 \vec{u}(t)=\mat{K}\vec{x}_k,  \,
 kT_s \leq t < (k+1)T_s. 
 \end{align}
 \end{theorem}
\begin{proof}
See Appendix~\ref{sec:proofs}
\end{proof}
